Evaluate PEER in each cohort and brain region

### 2021-03-10 combined_analysis/eval_resid_in_each.Rmd
add CTS

## Summarize samples
Note that these numbers are based on Ethnicity, rather then genetically determined ancestry used in the filtering for eQTL analysis.
```{r summary}
METADATA %>% group_by(Dx, Institution, Region) %>% dplyr::summarise(count = n()) %>% 
  kable(caption="Diagnosis, Institution, Region") %>% kable_styling(full_width=FALSE)

>>>>

## Summarize samples
Note that these numbers are based on Ethnicity, rather then genetically determined ancestry used in the filtering for eQTL analysis.
```{r summary}
METADATA %>% group_by(Dx, Institution, Region) %>% dplyr::summarise(count = n()) %>% ©
  kable(caption="Diagnosis, Institution, Region") %>% kable_styling(full_width=FALSE)
